Model-based variable selection for regression with highly correlated variables.

### 2014-05-01 www/article13.tex
up ident
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@564 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

First, we observe that if each variable in $\boldsymbol{X}_r$ is a Gaussian mixture, then there is at least one Gaussian mixture on the right of each sub-regression. So there is a non-empty subset of $\boldsymbol{X} \subset \boldsymbol{X}_f$ containing Gaussian mixtures. We note $\boldsymbol{X}_{S^c}$ its complement (empty or not) in $\boldsymbol{X}_f$

The theorem from Maugis guarantee that a sub-regression between Gaussian mixtures is identifiable.
		For each sub-regression, 

>>>>

First, we observe that if each variable in $\boldsymbol{X}_r$ is a Gaussian mixture, then there is at least one Gaussian mixture on the right of each sub-regression. So we have $\boldsymbol{X}^G \subsetneq \boldsymbol{X}_f$ containing Gaussian variables and we note the Gaussian mixtures $\boldsymbol{X}^{G^c}\neq \emptyset$ its complement in $\boldsymbol{X}_f$.

The theorem from Maugis guarantee that a sub-regression between Gaussian mixtures is identifiable.
		\begin{eqnarray}
			\forall j \in I_r, \boldsymbol{X}^j_{|\boldsymbol{X}^G,\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^G\boldsymbol{\alpha}_j^G+\boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c}+ \boldsymbol{\varepsilon}_j \\
			\boldsymbol{X}^j_{|\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c} + \tilde{\boldsymbol{\varepsilon}}_j \textrm{ is identifiable where} \\
			\tilde{\boldsymbol{\varepsilon}}_j&=&\boldsymbol{X}^{G}\boldsymbol{\alpha}_j^{G}+ \boldsymbol{\varepsilon}_j \textrm{ is Gaussian. And we have the unique decomposition} \\
			f(\boldsymbol{X}^j|\boldsymbol{X}^G,\boldsymbol{X}^{G^c})&=&f(\boldsymbol{X}^j|\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G})
		\end{eqnarray}
		We have the unique (Gaussian are allowed only on the right of the sub-regressions) decomposition $f(\boldsymbol{X}_r|\boldsymbol{X}_f)=f(\boldsymbol{X}_r|\boldsymbol{X}^G,\boldsymbol{X}^{G^c})=f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G}) $ 
		where  $f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})$ is identifiable. Moreover, $\boldsymbol{X}^{G}$ is a set (empty or not) of independent Gaussian variables, whose parameters are identifiable.
		So $\forall j \in I_r, f(\boldsymbol{X}^j|\boldsymbol{X}_f)$. And the structure is identifiable.
